Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis

### 2018-03-21 paper/finalish/article.tex
switch Jing to corresponding author
Add link to github islandR package

\author[1]{Sih-Jing Liao}

\author[1]{Jonathan Marshall*}

@@

\corres{*J Marshall, Institute of Fundamental Sciences, Massey University, Palmerston North, New Zealand. \email{J.C.marshall@massey.ac.nz}}

@@

>>>>

\author[1]{Sih-Jing Liao*}

\author[1]{Jonathan Marshall}

@@

\corres{*Sih-Jing Liao, Institute of Fundamental Sciences, Massey University, Palmerston North, New Zealand. \email{S.J.Liao@massey.ac.nz}}

@@

All code for fitting the genotype distributions, estimating attribution probabilities and producing figures, along with the data are available in the R package `islandR` from \url{https://github.com/jmarshallnz/islandR}.
